Hierarchical Reverberation Mapping

### 2013-12-03 Paper/ms.tex
Fixed error
More little edits

Each object in the sample had its own transfer function parameters. The upper
limit $b$ of the transfer function was simulated using a log-normal distribution
with a median value of 10 days, and the standard deviation of $\ln(b)$ was
0.3. Given $b$, $a$ was simulated from a uniform distribution between $0$ and
$a$. The resulting distribution of lags $\bar{\tau} = (a+b)/2$ is very well
approximated by a lognormal distribution with a median of 7.4 days and width
(quantified by the standard deviation of $\log_{10}(\bar{\tau})$) of 0.157
(these two quantities are the ones we will infer using the hierarchical model).
The response amplitudes $A$ and $C$ were set to 0.5 and 0 respectively, for
all objects.

The measured data for each of the 100 AGN was
continuum flux measurements, once per day, for 100 days. The continuum fluxes
for each object oscillate around a mean value of 50 in arbitrary units, and the
standard deviation of the measurement noise is 1 (i.e. 2\%). The line data is measured on
only two days, with times selected from a uniform distribution between $t=50$
and $t=100$ days (i.e. corresponding to the latter half of the continuum data).
The flux of the line data is typically about half that of the continuum data
(since $A=0.5$ for all objects), and the
measurement noise for the line data is 0.25, or about 1\%.
See Figure~\ref{fig:data} for three illustrative data sets from the sample.

>>>>

Each object in the sample had its own transfer function parameters. The upper
limit $b$ of the transfer function was simulated using a log-normal distribution
with a median value of 10 days, and the standard deviation of $\ln(b)$ was
0.3. Given $b$, $a$ was simulated from a uniform distribution between $0$ and
$b$. The resulting distribution of lags $\bar{\tau} = (a+b)/2$ is very well
approximated by a lognormal distribution with a median of 7.4 days and width
(quantified by the standard deviation of $\log_{10}(\bar{\tau})$) of 0.157
(these two quantities are the ones we will infer using the hierarchical model).
The response amplitudes $A$ and $C$ were set to 0.5 and 0 respectively, for
all objects.

The measured data for each of the 100 AGN was
continuum flux measurements, once per day, for 100 days. The standard deviation
of the measurement noise is 1 flux unit (i.e. 2\%). The line data is measured on
only two days, with times selected from a uniform distribution between $t=50$
and $t=100$ days (i.e. corresponding to the latter half of the continuum data).
The flux of the line data is typically about half that of the continuum data
(since $A=0.5$ for all objects), and the
measurement noise for the line data is 0.25 flux units, or about 1\%.
See Figure~\ref{fig:data} for three illustrative data sets from the sample.
